Cluster Dynamics with HETDEX at z < 0.5 - I: Simulated Performance, Mass Distribution and Limits

### 2016-03-02 ms.tex
first few casey comments

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
%\usepackage{times}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
% \usepackage{mathptmx}
% \usepackage{txfonts}

@@

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
\title[Short Title]{Cluster Dynamics with HETDEX - I: Simulated Performance, Mass Distribution and Limits}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[S. Boada et al.]{
Steven Boada,$^{1}$\thanks{E-mail: boada@physics.tamu.edu}
C.~Papovich,$^{1}$
R.~Wechsler,$^{2,3}$
T. S.~Li,$^{1}$\newauthor\phantom{x}
K.~Gebhardt,$^{4}$
E.~Rozo,$^{2}$
E. S.~Rykoff,$^{2}$
\\
% List of institutions
$^{1}$George P.\ and Cynthia Woods Mitchell Institute for
Fundamental Physics and Astronomy, Texas A\&M University, College Station, TX, 77843-4242\\
$^{2}$Kavli Institute for Particle Astrophysics and Cosmology, Department of Physics, Stanford University, Stanford, CA 94305, USA\\
$^{3}$Department of Particle Physics and Astrophysics, SLAC National Accelerator Laboratory, Menlo Park, CA 94025, USA\\
$^{4}$The University of Texas}

@@

Throughout this paper, we adopt the following cosmological model ($\Omega_\Lambda = 0.77$,
$\Omega_M = 0.23$, $\sigma_8 = 0.83$ and $H_0= 72$ \kms \mpc), assume a Chabrier initial mass function (IMF; \citealt{Chabrier2003}), and use AB magnitudes \citep{Oke1974}.

@@

The ``Buzzard'' mock galaxy catalogs (R. Wechsler et al., private communication) cover 375.68 \degsq\ between $60 < RA < 90$ and $-61 < DEC < -41$ and are derived from a combination of Sub-halo Abundance Matching (ShAM) and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) tied to an in house n-body cosmological simulation. A brief description of the catalog creation is described as follows. The initial conditions are generated with a second-order Lagrangian perturbation theory using {\tt 2LPTic} \citep{Crocce2006}. Dark matter (DM) n-body simulations are run using {\tt LGadget-2} (a version of {\tt Gadget-2}; \citealt{Springel2005}). The DM halos are identified using the {\tt ROCKSTAR} halo finder \citep{Behroozi2013} which also calculates halo masses and other various parameters.

>>>>

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
\usepackage{times}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
% \usepackage{mathptmx}
% \usepackage{txfonts}

@@

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
\title[Short Title]{Cluster Dynamics with HETDEX at z < 0.5 - I: Simulated Performance, Mass Distribution and Limits}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[S. Boada et al.]
{\parbox{\textwidth}{Steven Boada,$^{1}$\thanks{E-mail: boada@physics.tamu.edu}
C.~Papovich,$^{1}$
R.~Wechsler,$^{2,3}$
T. S.~Li,$^{1}$
K.~Gebhardt,$^{5}$
E.~Rozo,$^{2,4}$
E. S.~Rykoff,$^{2}$}\vspace{0.4cm}\
\\
\parbox{\textwidth}{$^{1}$George P.\ and Cynthia Woods Mitchell Institute for Fundamental Physics and Astronomy, and Department of Physics and Astronomy, Texas A\&M University, College Station, TX, 77843-4242, USA\\
$^{2}$Kavli Institute for Particle Astrophysics and Cosmology, Department of Physics, Stanford University, Stanford, CA 94305, USA\\
$^{3}$Department of Particle Physics and Astrophysics, SLAC National Accelerator Laboratory, Menlo Park, CA 94025, USA\\
$^{4}$Department of Physics, University of Arizona, Tucson, AZ 85721, USA\\
$^{5}$Department of Astronomy, The University of Texas at Austin, Austin, TX 78712, USA}}

@@

Throughout this paper, we adopt the following cosmological model: $\Omega_\Lambda = 0.714$,
$\Omega_M = 0.286$, $\sigma_8 = 0.82$ and $H_0= 70$ \kms \mpc (taken from the Buzzard catalogs; see below), assume a Chabrier initial mass function (IMF; \citealt{Chabrier2003}), and use AB magnitudes \citep{Oke1974}.

@@

The ``Buzzard'' mock galaxy catalogs (R. Wechsler et al., private communication) cover 375.68 \degsq\ between $4^h< RA < 6^h$ and $-61\degree < DEC < -41\degree$ and are derived from a combination of Sub-halo Abundance Matching (ShAM) and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) tied to an in house n-body cosmological simulation. A brief description of the catalog creation is described as follows. The initial conditions are generated with a second-order Lagrangian perturbation theory using {\tt 2LPTic} \citep{Crocce2006}. Dark matter (DM) n-body simulations are run using {\tt LGadget-2} (a version of {\tt Gadget-2}; \citealt{Springel2005}). The DM halos are identified using the {\tt ROCKSTAR} halo finder \citep{Behroozi2013} which also calculates halo masses and other various parameters.
